---
title: "Meta Analysis Multi-Level Model"
author: "Original: Rose Graves, Edited: Kelsey McDonald"
date: "6/3/2020"
output: html_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(dplyr)
library(meta)
library(dmetar)
library(metafor)
library(ggplot2)
```

Load Data
```{r}

load("C:/Users/krmcd/OneDrive - Duke University/Duke/Walter Sinnot-Armstrong/Meta Analysis/Analysis_Publication/ValenceMetaAnalysis-master/df.RData")

#this file now includes the online/in-person boolean for included studies
mydata2 <- read.csv("C:/Users/krmcd/OneDrive - Duke University/Duke/Walter Sinnot-Armstrong/Meta Analysis/Analysis_Publication/mydata2.csv") 

df$OnlineBool <- mydata2$OnlineSubjBool
```

### Make histogram of publication years to show time-trending interest on framing effects
```{r 'setup', echo = FALSE, cache = FALSE}

#trimdf <- df[!duplicated(df[c("Authors")]),]
#trimdf$PubYear <- as.numeric(trimdf$PubYear)
#ggplot(data=trimdf, aes(x=PubYear)) + geom_histogram() + 
#  labs(title="Empirical Articles on Framing Effects") +
#  theme(plot.title = element_text(hjust = 0.5)) +
#  labs(x="Year of Publication", y="Number of Publications")

```



### Carry out the Model with Sample as the third level (True Direction of Effect Size) for between-subjects and within-subjects design separately

```{r}
df_no_inter = df %>% filter(MainEffectvInteraction==1) #Removing all interaction terms
df_between = df %>% filter(betweeen_within_bin==1)
df_within = df %>% filter(betweeen_within_bin==0)

full.modelTrue.between <- rma.mv(data = df_between, y = ESTrue,
                    V = esvar,
                     random = ~ 1 | Authors/`Sample#`, 
                     tdist = TRUE,
                     method = "REML")

summary(full.modelTrue.between)
rma(data=df_between, y = ESTrue, esvar) #to calculate I2 and tau2



full.modelTrue.within <- rma.mv(data = df_within, y = ESTrue,
                    V = esvar,
                     random = ~ 1 | Authors/`Sample#`, 
                     tdist = TRUE,
                     method = "REML")
summary(full.modelTrue.within)
rma(data=df_within, y = ESTrue, esvar) ##to calculate I2 and tau2
```

### Make forest plot (Note for between-subs: save to pdf that is 8.5 x 30 inches to make sure labels are legible)
```{r}
forest(full.modelTrue.between, slab = df_between$StudyID, annotate=FALSE, cex=0.5, cex.lab=0.5, cex.axis=0.5, ylim=c(-1.5,285),top=7, mlab="Random Effects Estimate, Between-Subjects Studies", xlab="Cohen's d Effect Size")

forest(full.modelTrue.within, slab = df_within$StudyID, annotate=FALSE, mlab="Random Effects Estimate, Within-Subjects Studies", xlab="Cohen's d Effect Size")
```

#### Subgroup Analyses for Between-Subjects Dataset:




### Subgroup Analysis: Student vs Non-Student:
```{r}
df_between$student_bin <- factor(df_between$student_bin)

full.modelTrue.student <- rma.mv(data = df_between, y = ESTrue,
                    V = esvar,
                     random = ~ 1 | Authors/`Sample#`, 
                     tdist = TRUE,
                     method = "REML",
                    mods = ~student_bin)

summary(full.modelTrue.student)

```

### Subgroup Analysis: Online vs In-Person Studies
```{r}

full.modelTrue.onlinePerson <- rma.mv(data = df_between, y = ESTrue,
                    V = esvar,
                     random = ~ 1 | Authors/`Sample#`, 
                     tdist = TRUE,
                     method = "REML",
                    mods = ~OnlineBool)

summary(full.modelTrue.onlinePerson)

```

### Subgroup Analysis: Gender:
```{r}

full.modelTrue.gender <- rma.mv(data = df_between, y = ESTrue,
                    V = esvar,
                     random = ~ 1 | Authors/`Sample#`, 
                     tdist = TRUE,
                     method = "REML",
                    mods = ~PropMales)

summary(full.modelTrue.gender)

```

### Subgroup Analysis: Between vs within-subjects design: (between = 1, within = 0)
### This is not relevant since we're formally separating the datasets by this variable in the manuscript
```{r}
#df$betweeen_within_bin <- factor(df$betweeen_within_bin)
#df <- df[!is.na(df$betweeen_within_bin),]
#full.modelTrue.design <- rma.mv(data = df, y = ESTrue,
#                    V = esvar,
#                     random = ~ 1 | Authors/`Sample#`, 
#                     tdist = TRUE,
#                     method = "REML",
#                    mods = ~betweeen_within_bin)

#summary(full.modelTrue.design)

```


### Mortal v. NonMortal Absolute 

Comparing scenarios that involved possible loss of human lives (mortal), compared to scenarios that did not. 

```{r}
df_between$MortalVnonMortal <- as.integer(df_between$MortalVnonMortal)
mortalvnon.modelTrue <- rma.mv(data = df_between, y = ESTrue,
                    V = esvar,
                     random = ~ 1 | Authors/`Sample#`, 
                     test = "z",
                     method = "REML",
                    mods = ~MortalVnonMortal)

summary(mortalvnon.modelTrue)

#ggplot(data = df_no_inter, aes(x = ESTrue)) + geom_histogram() + facet_grid(.~MortalVnonMortal) + xlab("Effect Size")


```

NA cases were reserved for when there multiple scenarios presented to participants and some involved life and death while others did not. Also in the case of Alien lives. 

### ADP v. Other

This looks at scenarios that were specifically the original ADP problem, and compares them to all other scenarios.

#### Absolute Value of ES

```{r}

#df_no_inter$ADP_other_bin = as.numeric(df_no_inter$ADP_other_bin)

#ADPother.modelAbs <- rma.mv(data = df_no_inter, y = ES,
#                    V = esvar,
#                     random = ~ 1 | Authors/`Sample#`, 
#                     tdist = TRUE,
#                     method = "REML",
#                    mods = ~ADP_other_bin)

#summary(ADPother.modelAbs)

#ggplot(data = df_no_inter, aes(x = ES)) + geom_histogram() + facet_grid(.~ADP_other_bin) + xlab("Effect Size")

```

#### True Value ES

```{r}
df_between$ADP_other_bin = as.numeric(df_between$ADP_other_bin)
ADPother.modelTrue <- rma.mv(data = df_between, y = ESTrue,
                    V = esvar,
                     random = ~ 1 | Authors/`Sample#`, 
                     test = "z",
                     method = "REML",
                    mods = ~ADP_other_bin)

summary(ADPother.modelTrue)

#ggplot(data = df_no_inter, aes(x = ESTrue)) + geom_histogram() + facet_grid(.~ADP_other_bin) + xlab("Effect Size")

```

### ADP and ADPmodif v. Other

```{r}

df_adp_adpmodif <- df_between%>% dplyr::filter( grepl('ADPModif|ADP', MoralJudgeFactor))
df_adp_adpmodif <- df_adp_adpmodif%>% dplyr::mutate(moraljudge_bin = ifelse(MoralJudgeFactor =="ADP", 1,0))
df_adp_adpmodif$moraljudge_bin = as.numeric(df_adp_adpmodif$moraljudge_bin)


ADPmodmodel <- rma.mv(data = df_adp_adpmodif, y = ESTrue,
                    V = esvar,
                     random = ~ 1 | Authors/`Sample#`, 
                     test = "z",
                     method = "REML",
                    mods = ~moraljudge_bin)

summary(ADPmodmodel)

#ggplot(data = df_no_inter_adp_adpmodif, aes(x = ESTrue)) + geom_histogram() + facet_grid(.~MoralJudgeFactor) + xlab("Effect Size")

```

```{r}
m_RE <- metagen(ESTrue,
                data=df_between,
                lower = lowCI,
                upper = highCI,
                studlab=paste(StudyID),
                comb.fixed = FALSE,
                comb.random = TRUE,
                method.tau = "SJ",
                hakn = TRUE,
                prediction=TRUE,
                sm="SMD")
```

### Assess publication bias
```{r}
funnel(m_RE, xlab="Cohen's d", contour=c(.95,.975,.99), col.contour=c("darkgreen","green","lightgreen")) +
  legend("bottomright", c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
         fill=c("darkgreen","green","lightgreen"))
```

### Run Egger's Test and trimfill procedure
```{r}
eggers.test(x=m_RE)
trimfill(m_RE)
```



